---
title: "Class 02: R Intro"
author: "Amanda White"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: TRUE
    toc_float: TRUE
    number_sections: FALSE
    code_folding: show
    code_download: TRUE
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment

R has three assignment operators:

- `->`
- `=`
- `<-`

```{r assignments}
x1 <- 5
x2 = 5
7 -> x3


cat("The value of x1 is:", x1)
```

## Atomic Vectors

Atomic vectors are one-dimensional data structures where all values in them have to have the same data type

```{r atomic, results='hold'}

mixed_vector <- c('ISA' , 401)

mixed_num <- c(401L, 3.14159) #the 'L' means that you are making the integer a double

typeof(mixed_vector)
typeof(mixed_num)
```

From this output, if you have multiple data types, R will use the most general representation of them. 


## Lists

Subsetting a list is one of the most common sources of errors in this class.

```{r}
list1 <- list( # list constructor/creator
  1:3, # atomic double/numeric vector  of length = 3
  "a", # atomic character vector of length = 1 (aka scalar)
  c(TRUE, FALSE, TRUE), # atomic logical vector of length = 3
  c(2.3, 5.9) # atomic double/numeric vector of length =3
)
list1 # printing the list

from_list_to_sublist1 <- list1[1]
from_list_to_sublist3 <- list1[3]

from_list_to_underlying_structure <- list1[[2]]
```



